## Reproducibility

### Code document - `quarto`

The code in quarto document format is included below which can be used to render and rerun this analysis workflow in its entirety. It can be rendered with the `quarto` publishing system running in the R programming environment in the `renv` section. You can download the file using the button below.

```{r qmd-download}
#| echo: false
#| results: "asis"

qmd_embed_download()

```

### R programming environment - `renv`

This project uses `renv` to manage package dependencies. `renv` is an R package that helps create and manage project-specific environments, ensuring that the correct versions of packages are used for reproducibility. To restore the environment, you would typically run `renv::restore()` in your R session, which will install the packages specified in the `renv.lock` file.
You can download the `renv.lock` file below to restore the environment.

```{r renv-download}
#| echo: false
#| results: "asis"

renv_embed_download()

```

The current status of the environment is as follows:

```{r, renv-status}
renv::status()
```

### Session info

```{r session-info}
sessionInfo()
```

---

```{r render-time}
#| echo: false
#| results: "asis"
end_time <- Sys.time()
render_duration <- end_time - start_time

cat("Document render completed at:", format(end_time, "%Y-%m-%d %H:%M:%S"), "\n\n")
cat("Total render time:", round(as.numeric(render_duration, units = "mins"), 2), "minutes\n")
```
